---
classoption: a4paper, oneside
documentclass: book
fontsize: 11pt
geometry: margin=1in
linestrech: 1.5
linkcolor: black
citecolor: black
urlcolor: black
toccolor: black
bibliography: references.bib
subparagraph: TRUE
mainfont: Arial
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
    number_sections: yes
header-includes:
- \usepackage{array, amsmath, titlesec, fancyhdr, pageslts}
- \usepackage[justification=justified, singlelinecheck=false, labelsep=period, labelfont=bf]{caption}
- \renewcommand{\arraystretch}{1.0}
- \setlength{\extrarowheight}{1pt}
- \titleformat{\chapter}{\normalfont\huge}{\thechapter.}{20pt}{\huge\bf}
- \renewcommand{\chaptername}{}
- \let\origappendix\appendix
- \renewcommand\appendix{\clearpage\pagenumbering{roman}\origappendix}
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.path = 'figures/', echo = FALSE, warning = FALSE, message = FALSE)
```

\frontmatter

```{r child = 'sections/title.Rmd'}
```

\pagestyle{fancy}
\fancyhead{}
\fancyfoot[CE,CO]{\thepage}
\renewcommand{\headrulewidth}{0.0pt}

```{r child = 'sections/acknowledgements.Rmd'}
```

\newpage

```{r child = 'sections/abstract.Rmd'}
```

\newpage
\setcounter{tocdepth}{1}
\tableofcontents

\newpage
\listoffigures
\addcontentsline{toc}{chapter}{List of Figures}

\newpage
\listoftables
\addcontentsline{toc}{chapter}{List of Tables}

\mainmatter
\fancyhead[R]{\footnotesize\leftmark}
\newpage
```{r child = 'sections/introduction.Rmd'}
```

\newpage
```{r child = 'sections/chapter02.Rmd'}
```

\newpage
```{r child = 'sections/chapter03.Rmd'}
```

\newpage

\appendix
```{r child = 'sections/appendix.Rmd'}
```

\backmatter

# References